ms2

### 2017-10-10 ms2/ms2_display.Rmd
ms2: try combining

@@

```{r hrr_linear_fnz_table}
results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable
```

@@

```{r hrr_linear_mup_table}
results %>%
  filter(model=='univariate_mup', unit_type=='hrr', term=='mup') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable
```

@@

>>>>

ineq_hrr_mean = ineq %>%
  filter(unit_type=='hrr') %>%
  group_by(drug_group) %>%
  summarize_at(vars(mean, fnz, mup), mean)

@@

```{r hrr_linear_fnz_table}
results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable

results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable
```

@@

```{r hrr_linear_mup_table}
results %>%
  filter(model=='univariate_mup', unit_type=='hrr', term=='mup') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  # swo: fanciful now
  left_join(ineq_hrr_mean, by='drug_group') %>%
  mutate(dR_nu_ext=-(mup-1)/fnz*estimate,
         dR_nu_int=estimate/fnz) %>%
  select(bug, drug_group, estimate, anova.p.value, dR_nu_ext, dR_nu_int) %>%
  kable
```

@@

### Effect of both together

```{r both_effects}
results %>%
  filter(unit_type=='hrr', model=='multivariate_fnz_mup', term != '(Intercept)') %>%
  select(bug, drug_group, term, estimate) %>%
  spread(term, estimate) %>%
  rename(beta_fnz=fnz, beta_mup=mup) %>%
  left_join(ineq_hrr_mean, by='drug_group') %>%
  mutate(dR_ext=beta_fnz - (mup - 1)/fnz * beta_mup,
         dR_int=beta_mup / fnz) %>%
  kable
```
